\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-28 tex/ms.tex
stuff

For each of the two sectors considered, we downloaded a random subsample of 
1,000 short-cadence lightcurve files corresponding to postage stamps located 
across the full \TESS field of view and extracted the background flux time 
series from each. 
Not all postage stamps are equally informative, since the desired signal from 
Sol d is inhomogenously spread across the \TESS detectors and manifests 
differently in different regions (see \S\ref{sec:systematics}). 
We down-selected our pool of 1000 targets to 75 maximally useful background 
lightcurves from Sector 1 and 20 from Sector 2. 
This down-selection was done with several criteria in mind: each lightcurve 
should contain a significant signal from Sol d; they should be representative 
of the general background flux modulation seen across the \TESS cameras, rather 
than containing any truly localized signals from astrophysical background 
sources; and the sample as a whole should contain the full range of typical 
behaviors of background across the entire \TESS field of view. 
To accomplish this, we... \todo{(decide whether it's outlier rejection only or 
full-on categorization)}

@@

Second, while we attempted to adopt agnostic priors on the map coefficients---i.e.,
we fit for a spectral slope rather than impose one---our inferred map is still 
heavily prior-dependent. Our choice of regularization strength for the systematics
was based on trial-and-error and what ``looked good'', as was the choice for the 
hyperprior on the spectral
slope and the maximum spherical harmonic degree of the map. Although the main
features of the map (the monsoon over south Asia, the clouds over Africa and
South America, and dark regions associated with the three major oceans) persist
regardless of the choice of prior, their exact shapes and contrast varied
significantly under different assumptions.

@@

\todo{(summarize)}
\todo{(talk abt prospects for doing this analysis with exoplanets)}

\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully 
acknowledge Dan Foreman-Mackey, David W Hogg, Ben Pope, \todo{and ...} 
for useful conversations. Crucial parts of this work were carried out at the 
TESS Data Workshop, hosted by Space Telescope Science Institute, and the 
Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, 
TensorFlow \citep{Abadi2015}, \spiceypy \citep{Annex2019}}
% Bibliography
\pagebreak
\bibliography{bib}

>>>>

For each of the two sectors considered, we downloaded a random subsample of 
1,000 short-cadence lightcurve files corresponding to postage stamps located 
across the full \TESS field of view and extracted the background flux time 
series from each. 
Not all postage stamps are equally informative, since the desired signal from 
Sol d is inhomogenously spread across the \TESS detectors and manifests 
differently in different regions (see \S\ref{sec:systematics}). 
We down-selected our pool of 1,000 targets to 75 maximally useful background 
lightcurves from Sector 1 and 20 from Sector 2. 
This down-selection was done with several criteria in mind: each lightcurve 
should contain a significant signal from Sol d; they should be representative 
of the general background flux modulation seen across the \TESS cameras, rather 
than containing any truly localized signals from astrophysical background 
sources; and the sample as a whole should contain the full range of typical 
behaviors of background across the entire \TESS field of view. 
To accomplish this, we... \todo{(decide whether it's outlier rejection only or 
full-on categorization)}

@@

Second, while we attempted to adopt agnostic priors on the map coefficients---i.e.,
we fit for a spectral slope rather than impose one---our inferred map is still 
heavily prior-dependent. Our choice of regularization strength for the systematics
was based on trial-and-error and what ``looked good,'' as was the choice for the 
hyperprior on the spectral
slope and the maximum spherical harmonic degree of the map. Although the main
features of the map (the monsoon over south Asia, the clouds over Africa and
South America, and dark regions associated with the three major oceans) persist
regardless of the choice of prior, their exact shapes and contrast varied
significantly under different assumptions.

@@

We have used \TESS photometry to
produce a global map of Sol d, a terrestrial planet in the habitable
zone of a G2 main-sequence star. We adapted the \starry code to 
generate (and invert) light curves in reflected light, coupling it
to a variation of pixel level decorrelation to model the systematics
in the \TESS detector. We detect three large scale bright regions near
the equator of the planet, associated with persistent cloud structures
at longitudes of $-60^\circ$, $+30^\circ$, and $+90^\circ$, which
likely track continents. Pronounced dark features are identified
at longitudes of $\pm 180^\circ$, $-30^\circ$, and $+60^\circ$ with
significant latitudinal extent, likely tracking oceans. Because of the
vantage point of \TESS during Sectors 1 and 2, we are not sensitive to
high latitudes on the planet, although this may change with upcoming
sectors.

\todo{A bit more here.}

\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully 
acknowledge Dan Foreman-Mackey, David W. Hogg, Ben Pope, \todo{and ...} 
for useful conversations. Crucial parts of this work were carried out at the 
TESS Data Workshop, hosted by Space Telescope Science Institute, and the 
Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, 
TensorFlow \citep{Abadi2015}, \spiceypy \citep{Annex2019}}

% Bibliography
\bibliography{bib}
